### 2020-03-10 short.body.tex
two more citations!

Much is still unknown about the time scale and effectiveness of asymptomatic transmission in COVID-19. 
Here we highlight the need to characterize the generation-interval distribution for asymptomatic transmission, and its consequences not only for contact tracing but for estimation of the basic reproduction number of the ongoing COVID-19 outbreak~\citep{park_preprint} and of the effective proportion of asymptomatic transmission during the exponential-growth phase.
Our reproductive number findings fit into a broader framework linking epidemic speed, strength, and generation intervals -- for a given observed speed increases in the mean generation interval imply larger reproduction number~\citep{wallinga2007generation, powers2014impact, park_2019practical}.

>>>>

Much is still unknown about the time scale and effectiveness of asymptomatic transmission in COVID-19. 
Here we highlight the need to characterize the generation-interval distribution for asymptomatic transmission, and its consequences not only for contact tracing but for estimation of the basic reproduction number of the ongoing COVID-19 outbreak~\citep{park_preprint} and of the effective proportion of asymptomatic transmission during the exponential-growth phase.
Our reproductive number findings fit into a broader framework linking epidemic speed, strength, and generation intervals -- for a given observed speed increases in the mean generation interval imply larger reproduction number~\citep{wearing2005appropriate, roberts2007model, wallinga2007generation, powers2014impact, park_2019practical}.
